Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-08 main.tex
started writing the dynamic experiments, WIP

    \subsection{Results \skug{Full: 3, Polished: 2}}
    \subsubsection{Static experiments}
    \paragraph{Small cluster}

   On the small cluster, \heft could produce valid assignments in $14$ experiments out of $290$ ($4.8\%$).
    The successful schedules were achieved almost exclusively on the tiny workflows and one one 200-task workflow.
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm could schedule
    $94.9\%$ of workflows, thus having the smallest failure rate of $5\%$.

    \paragraph{Normal cluster}

@@

    The relative makespans are $14-29$\% worse for small workflows, $22-40$\% worse on middle-sized workflows and $16-35$\%
    on big workflows.
    \wrt failures, all heuristics again manage to schedule all workflows.
    \subsubsection{Behavior of workflow types when scaling workflow size}
    \subsubsection{Running times}
    The geometric means of runtimes of all heuristics on small workflows lie between $0.9$ and $2.2$ seconds.
    For middle-sized workflows, the runtimes for \heftbl and \heftblc are close to $2$ minutes, while \heftmm
    takes $5.1$ minutes.
    For the big workflows, again, \heftbl and \heftblc show a better runtime ($5$ and $5.4$ minutes, respectively).
    \heftmm takes $13.9$ minutes on average.
    \subsubsection{Summary}

>>>>

    \subsection{Results \skug{Full: 3, Polished: 2}}
    \subsubsection{Static experiments}
    \paragraph{Tiny cluster}

    On the tiny cluster, \heft could produce valid assignments in $14$ experiments out of $290$ ($4.8\%$).
    The successful schedules were achieved almost exclusively on the tiny workflows and one one 200-task workflow.
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm could schedule
    $94.9\%$ of workflows, thus having the smallest failure rate of $5\%$.

    \paragraph{Normal cluster}
    \skug{OLD DATA here, rewrite}

@@

    The relative makespans are $14-29$\% worse for small workflows, $22-40$\% worse on middle-sized workflows and $16-35$\%
    on big workflows.
    \wrt failures, all heuristics again manage to schedule all workflows.
    \subsubsection{Behavior of workflow types when scaling workflow size}
    \subsubsection{Running times}
    The geometric means of runtimes of all heuristics on small workflows lie between $0.9$ and $2.2$ seconds.
    For middle-sized workflows, the runtimes for \heftbl and \heftblc are close to $2$ minutes, while \heftmm
    takes $5.1$ minutes.
    For the big workflows, again, \heftbl and \heftblc show a better runtime ($5$ and $5.4$ minutes, respectively).
    \heftmm takes $13.9$ minutes on average.
    \subsubsection{Dynamic experiments}
    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 20 experiments out of 290 ended with a valid makespan
    in case of \heftbl, 33 in case of \heftblc and 29 in case of \heftmm.
    In case of \heftmm, the makespan without recomputation would have been, on average, $5.77$ times longer than with the recomputation.

    \subsubsection{Summary}
